%----PrefaceImport----%
\documentclass{article}
\usepackage{fancyhdr}
\usepackage[a4paper,margin=1in,headsep=25pt]{geometry}
\usepackage{lipsum,hyperref}
\usepackage{enumerate,fullpage,proof}
\usepackage[fontsize=12pt]{fontsize}
\usepackage{amsmath,amscd,amsbsy,amssymb,latexsym,url,bm,amsthm}
\usepackage{epsfig,graphicx,subfigure}
\usepackage{listings}
\usepackage[usenames]{xcolor}

\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}

\pagestyle{fancy}
\pagenumbering{Alph}
\setlength{\headheight}{36.0pt}
\headsep = 25pt
\fancyhf{}
\lhead{CSE 4392/5369 Special Topic: Natural Language Processing}
\rhead{Homework 1: Introduction}
\lfoot{2026 Kenny Zhu}
%----Documentation----%
\begin{document}

\title{CSE 4392/5369 Special Topic: Natural Language Processing}
\author{Homework 1 - Spring 2026}
\date{Due Date: Jan 19, 2026, 11:59 PM}
\maketitle
\thispagestyle{fancy}

%----Homeworks----%

\section*{Problem 1 - 50\%}

Please read the following carefully and put your name and ID number
in all the places indicated to acknowledge that you have understood it.

\subsection*{Honor Code Acknowledgement:}
\textit{I pledge, on my honor, to uphold UT Arlington’s tradition of academic integrity, a tradition that
values hard work and honest effort in the pursuit of academic excellence.\\
\newline
I promise that I will submit only work that I personally create or contribute to group collaborations,
and I will appropriately reference any work from other sources. I will follow the highest standards
of integrity and uphold the spirit of the Honor Code.}\\
\newline
As a student enrolled in CSE 4392/5369, I will adhere to the UT Arlington Honor Code given above.\\
\newline
Name:\\
Student ID:\\

\subsection*{Assignment Policy Acknowledgement:}
\textit{There will be several homework assignments in this course. Most of the tasks will require
handwritten or typed solutions. Some assignments may have programming tasks. The solution to
programming tasks can be programmed in base versions of specific programming language which will be specify in homeworks. 
\textbf{All homework submissions must be submitted via Canvas. No other method of
submission accepted under any circumstances.} All homework scores (other than the lowest
one) will contribute to your final grade. If you find yourself in an emergency and cannot deliver
homework on time, immediately inform the instructor. Also, while working with other persons on
non-graded example problems from the textbook is a good way to help you develop your
understanding and insight into the techniques of problem solving, homework solutions must be
your work only. Violations of this will not be tolerated and result in severe penalties for all parties
involved, in strict compliance to official UTA policy.}\\
\newline
\textit{The points each assignment graded out of will be provided as part of its description. Assignments
submitted late will be automatically penalized, at a rate of \textbf{30\% of assignment max points per
day late. Late submission will not be accepted 2 days after due date.} Note that for some
assignments, submissions may not be accepted after the deadline (such assignments will
be announced in class beforehand). The submission due time (and the time the link will be
available till) will be shown in homeworks and Canvas. Exceptions will only be made for documented emergencies,
in strict adherence to UTA policy. Computer/Network crashes, Submission of Incomplete files,
Submission of Incorrect Files, Submitting at Incorrect Link are NOT acceptable excuses for late
submissions. \textbf{No exceptions will be made.} To avoid problems with such crashes and last-minute
problems, students are encouraged to submit as early as possible. They are also advised to
ensure that their file was uploaded correctly before submitting it. You can always revise your
submission till the deadline. If you are unable to work on/submit an assignment due to a valid
documented reason (illness, critical family emergencies, military service obligations, observance
of major religious holidays, and certain university service commitments) one makeup assignment
may be provided that will be due during finals week.}\\
\newline
As a student enrolled in CSE 4392/5369, I have read and understood the assignment policy
described above.\\
\newline
Name:\\
Student ID:\\

\subsection*{Academic Dishonesty Policy Acknowledgement:}
\textit{If you are caught colluding or copying in the assignments or exams the following consequences will
be applied.}\\
\textit{Per offence:}
\begin{itemize}
    \item You will be given a score of 0 points for that assignment or exam.
    \item Your final grade will be reduced by 2 letter grades (Up to a minimum of F)
    \item An academic integrity violation form will be filed.
    \begin{itemize}
        \item If you agree to sign the form
        \begin{itemize}
            \item You will be placed on disciplinary probation for 1 year and a 7 year reportable
            disciplinary record will be created.
            \item Additional violations may result in increasing sanctions up to and including
            suspension or expulsion.
        \end{itemize}
        \item If you do not agree to sign the form
        \begin{itemize}
            \item You will be temporarily given a grade of Incomplete (I)
            \item The Office of Academic Integrity will conduct a formal investigation based on
            evidence provided
            \item Based on decision, either the grade will be calculated with the penalty and with
            the consequences discussed above or grade will be calculated without
            penalties and no forms being filed.
        \end{itemize}
    \end{itemize}
\end{itemize}
\textit{This policy is not up for discussion/negotiation \textbf{under any circumstances}.}
\newline
As a student enrolled in CSE 4392/5369, I have read and understood the academic dishonesty policy
described above.\\
\newline
Name:\\
Student ID:\\


\section*{Problem 2 - 10\%}
Find a team mate for your Project! 
Please write down the names of your team members (including yourself):\\
Team Member 1 (my name):\\
Team Member 2 (my team mate's name, optional):\\
Team Member 3 (my team mate's name, optional):

\section*{Problem 3 -- 20\%}

This problem focuses on understanding different types of ambiguity in natural language, as discussed in class.

\begin{enumerate}
    \item \textbf{Types of Ambiguity}
    
    Based on the four types of ambiguity introduced in class (e.g., lexical ambiguity, syntactic ambiguity, semantic ambiguity, and discourse ambiguity), complete the following tasks:
    
    \begin{itemize}
        \item For each type of ambiguity, provide \textbf{two example sentences}.
        \item For each example, briefly explain the different possible interpretations and why it is classified as this type of ambiguity.
    \end{itemize}

    \item \textbf{Reflection Question}
    
    Answer the following questions based on your examples:
    \begin{itemize}
        \item Which type of ambiguity do you think is the most difficult for NLP systems to handle? Why?
    \end{itemize}
\end{enumerate}

\section*{Problem 4 -- 20\%}

This problem aims to help you become familiar with common NLP tasks and their real-world applications.

\begin{enumerate}
    \item \textbf{Understanding NLP Tasks}
    
    From the given list of NLP tasks (Text Classification, Named Entity Recognition, Machine Translation, Text Generation, Question Answering, 
    Speech Recognition, Text Summarization, Sentiment Analysis), choose \textbf{five} different NLP tasks.  
    For each selected task, briefly answer the following questions:
    \begin{itemize}
        \item What is the input to this task?
        \item What is the output of this task?
        \item Describe one real-world application scenario where this task is used.
    \end{itemize}

    \item \textbf{Experiencing Existing NLP Systems}
    
    From the five tasks you selected above, choose \textbf{two} tasks and explore existing NLP tools or systems.
    For each chosen task:
    \begin{itemize}
        \item Provide one or two example inputs.
        \item Show the corresponding outputs produced by the system.
    \end{itemize}

    \item \textbf{Reflection Question}
    
    Based on the NLP tasks you selected, which task do you think is the most complex, and why?
\end{enumerate}

\vspace{0.8em}
\noindent{\color{red}\footnotesize
\textbf{Submission Format:}
Submit the \texttt{.pdf} version of your homework (typed submissions are preferred;
Scanned images must be readable) via Canvas. File must be named
\texttt{lastname\_studentID\_hw1.pdf}.
}

\end{document}
