%----PrefaceImport----%
\documentclass{article}
\usepackage{fancyhdr}
\usepackage[a4paper,margin=1in,headsep=25pt]{geometry}
\usepackage{lipsum,hyperref}
\usepackage{enumerate,fullpage,proof}
\usepackage[fontsize=12pt]{fontsize}
\usepackage{amsmath,amscd,amsbsy,amssymb,latexsym,url,bm,amsthm}
\usepackage{epsfig,graphicx,subfigure}
\usepackage{listings}
\usepackage[usenames]{xcolor}

\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}

\pagestyle{fancy}
\pagenumbering{Alph}
\setlength{\headheight}{36.0pt}
\headsep = 25pt
\fancyhf{}
\lhead{CSE 3302/5307 Programming Language Concepts}
\rhead{Homework12:Object-oriented}
\lfoot{2023 Kenny Zhu}
%----Documentation----%
\begin{document}

\title{CSE 3302/5307 Programming Language Concepts}
\author{Homework12 - Fall 2023}
\date{Due Date: Nev.18, 2023, 11:59p.m. Central Time}
\maketitle
\thispagestyle{fancy}

%----Homeworks----%

\section*{Problem1 - 40\%}

Use Ada\footnote{You can use this online website: \href{https://www.tutorialspoint.com/compile_ada_online.php}{\textbf{https://www.tutorialspoint.com/compile\_ada\_online.php}}} language to implement a max heap (of int type) data type by array, it should have following methods:
\begin{itemize}
    \item empty:whether it is an empty heap
    \item size:return the size of the heap
    \item push:add a element into heap
    \item pop:remove the top element from heap
    \item top:access to the top element in heap
\end{itemize}
For testing: 

1.push 3

2.push 1

3.push 2

4.call size(), print size

5.call top(), print result

6.call pop()

7.repeat 5

8.call empty()

9.repeat 4


\section*{Problem2 - 60\%}

Suppose we have two strings: $x=CTACCG$ and $y=TACATG$. After an alignment, we have:

\begin{align*}
    &\ 1\ \ 2\ \ 3\ \ 4\ \ 5\ \ 6\ \ 7\\
    &\ C\ T\ A\ C\ C\ -\ G\\
    &-\ T\ A\ C\ A\ \ T\ G\\
\end{align*}

Here "$-$" means empty. In order to compare the distance between two strings, we usually use edit distance. There are two kind of penalties in edit distance.
\begin{itemize}
    \item Gap: If in alignment, we match a character with empty(such as position 1 and 6), there will be a gap penalty.
    
    \item Mismatch: If in alignment, we match a character with a different character(such as position 5), there will be a mismatch penalty.
\end{itemize} 

The alignment cost $C$ is define as:

\begin{equation*}
    C = \sum_{gap\ pair}Gap\ Penalty + \sum_{mismatch\ pair}Mismatch\ Penalty
\end{equation*}

Suppose in this case, the gap penalty is $a$ and the mismatch penalty is $b$, then the cost for this alignment is:
\begin{equation*}
    C = 2a+b
\end{equation*}

In \textbf{String Similarity} problem, we want to find the minimum alignment and its cost for two strings. We can use dynamic programming to solve this problem in $O(mn)$ space and $O(mn)$ time, where $m$ and $n$ are the length of the string. Actually there is a better algorithm called \textbf{Hirschberg Algorithm} which can solve this problem in $O(m+n)$ space and $O(mn)$ time.

~\\
The idea of Hirschberg Algorithm is we can combine divide and conquer with dynamic programming. Suppose we have two strings: $x_{1,...,n}$ and $y_{1,...,m}$. First we divide string $x$ into two sub strings: $x_{left} = x_{1,...,n/2}$ and $x_{right} = x_{n/2+1,...,n}$. Then we divide string $y$ at position $k$ into two sub strings: $y_{left} = y_{1,...,k}$ and $y_{right} = y_{k+1,...,m}$. We calculate the costs for $(x_{left}, y_{left})$ and $(x_{right}, y_{right})$ by divide and conquer. 
\begin{equation*}
    C_k=C(x_{left}, y_{left}) + C(x_{right}, y_{right})
\end{equation*}
We traverse $k$ from $0$ to $m$ to find the optimal $k_{opt}$ which leads to the minimum cost.
\begin{equation*}
    k_{opt} = \min_{k=0,...,m}C_k
\end{equation*}

In this problem, you are to find the lowest alignment cost between 2 string sequences. There are only uppercase letters in strings. The mismatch penalty of two letters are the distance between their order in ASCII. For example, $Distance(A, E) = 4$. The gap penalty is fixed as $7$. 
\begin{enumerate}[a)]
\item Implement a Hirschberg Algorithm to solve this problem with Smalltalk\footnote{You can use this online website: \href{https://www.tutorialspoint.com/execute_smalltalk_online.php}{\textbf{https://www.tutorialspoint.com/execute\_smalltalk\_online.php}}}.

\item Test your program with following inputs:
\begin{align*}
    &x=CTACPG\\
    &y=TACATG
\end{align*}
Your program should print the lowest cost and the aligned strings(add "$-$" into the strings to represent empty)
\end{enumerate}

\end{document}